---
title: "Activity #2: Simulating Random Processes"
author: ""
date: ""
output: 
  word_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

## Simulating "Smelling Parkinsons" 

```{r}
results <- do(10000) * rflip(12)

tally(~heads, data=results)


```
```{r}
histogram(~heads, width = 1, data=results)

```
  
  How likely would it be to get 11 or 12 heads when I flip a coin 12 times? 
  That's like Joy is guessing.  

```{r}
(pvalue <- (11+6)/10000)

```
The p-value is 0.017.  This is the probability that we would observe 11 or 12 heads if we flip a coin 12 times and repeat that many many times.  
  
  Since this probability is so small, we can conclude that while it is possible to see 11 or 12 correct answers if Joy is guessing, this is not likely. 
  
  
## Lady Tasting Tea

Simulate a lady tasting tea.  Assume that she is guessing (e.g. flipping a coin).  We will give her 8 cups of tea and record a H (if she gets it right) and a T (if she gets it wrong). 

(1)   flip a coin 8 times and do that lots of times. 
(2) tally how many head we got (distribution)
(3) Draw a histogram to show the distribution
(4) Compute the p-value, which will be the probability that we would observe 8 correct results (heads) if the lady is guessing. 


```{r}
results <- do(10000) * rflip(8)

tally(~heads, data=results)


```

  
```{r}
histogram(~heads, width = 1, data=results)
```
  
  
```{r}
(pvalue <- (35)/10000)
```

