---
title: "Biased and Unbiased Sampling"
author: ""
date: ""
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

## Objective

The objective of this exploration is to understand the difference between a biased sample and an unbiased sample. 


## Scenario #1: Gettysburg Address

List the words you selected from the Gettysburg Address: 

>Delete this text and type the words, separated by commas
  
Based on your sample of the 10 words above, what would you estimate is the length of an average word in the Gettysburg Address?  (Don't do any calculations, just make a guess) 

> Type your answer here

Do you think that your sample is representative of all words in the Gettysburg Address? 

> Type your answer here

## Gettysburg - Your Sample

Using the words in your sample, let's compute some numerical estimates. 


```{r}

```

> Describe average length of word and proportion of words containing letter E. 

## Gettysburg - Random Sample

Now let's take a **random** sample of the words in the Gettysburg Address and compute some numerical estimates.

```{r}

words <- read.csv("gettysburgWords(1).csv", header=T, sep = " ")

str(words)



```

> Describe average length of word and proportion of words containing letter E. 


Identify each of the following terms for the above scenario : 

What is the population of interest?   
> Type your answer here

What is the sample? 
> Type your answer here

What are the two parameters of interest? 
> Type your answer here 

What are the two statistics? 
> Type your answer here

Explain how the sample you chose (your 10 words) may have been biased. 
> Type your answer here


## Scenario 2:  English Language

OK, now let's think about the more general case.  How long do you think a typical word is in the **English Language**? 

> Type your answer here  


Now we have a different population of **words in the English Language".  Let's use the Gettysburg Address as a sample of size 268.  

```{r}

```

>


What is the population of interest (be sure to use the word "all")?   
> Type your answer here

What is the sample? 
> Type your answer here

What are the two parameters of interest? 
> Type your answer here 

What are the two statistics? 
> Type your answer here
  
Explain at least one way in which this sample might be biased. 

> Type your answer here

